Ecological network control

### 2018-06-18 paper/supp-info.Rmd
Plot Standard deviations for correlogram

```{r fig-correlogram, fig.width=fig_sizes()[[1]], fig.height=fig_sizes()[[1]], fig.cap="Mean Spearman correlation coefficients between control metrics (control capcity $\\phi$ and the likelyhood of being a superior node $\\sigma$) and centrality metrics commonly used to estimate a species' 'keystoness' (closeness centrality $l$ , betwenness $w$, eigen centrality $e$, page rank $g$ and degre $k$) in each of the networks. Purple and orange tiles indicate a positive correlation or negative correlation respectively."}
drake::loadd(fig_correlation)
fig_correlation[[1]]
```

>>>>

```{r fig-correlogram, fig.width=fig_sizes()[[2]], fig.height=fig_sizes()[[1]], fig.cap="Mean Spearman correlation coefficients between control metrics (control capcity $\\phi$ and the likelyhood of being a superior node $\\sigma$) and centrality metrics commonly used to estimate a species' 'keystoness' (closeness centrality $l$ , betwenness $w$, eigen centrality $e$, page rank $g$ and degre $k$) in each of the networks. Purple and orange tiles indicate a positive correlation or negative correlation respectively."}
drake::loadd(fig_correlation)
cowplot::plot_grid(plotlist = fig_correlation, ncol = 2)
```
